% !TEX root = ../main.tex
\section{Introduction}%
\label{sec:intro}

Modern \ac{CAD} tools include substantial support for parametric operations and
\ac{GCS}.  These mechanisms have been developed over the past few
decades~\cite{Bettig:2011:GCSPC} and are heavily and ubiquitously used across
the Architecture, Engineering, and Construction industry.

Parametric modeling is used to design with constraints.  Users express a set of
parameters and operations, establishing restrictions between geometric entities.
The resulting geometry can be controlled from input parameters using two
computational mechanisms:
\begin{enumerate*}[label= (\arabic*)]
  \item parametric operations, and
  \item \ac{GCS}.
\end{enumerate*}

However, traditional interactive methods for parametric modeling suffer from the
disadvantage that they do not scale properly when designing more complex ideas.
In recent years, a novel approach to design named \ac{AD} has emerged, allowing
the specification of sketches and models through
algorithms~\cite{McCormack:2004:GDPDR} using either a \ac{TPL}, a \acp{VPL}, or
even a mixture of both.

Dealing with \acp{GC} can still prove to be an arduous task.  Some operations,
such as point distance and tangency, must be handled carefully due to numerical
robustness issues that may arise during computation.  This means that, on top of
the design process itself, the user must spend additional time identifying and
carefully researching how to robustly implement solutions to \acp{GC}.

To overcome this problem, this report proposes the implementation of \ac{GC}
primitives with specialized efficient solutions for different combinations of
input objects.  We additionally focus our work around \acp{TPL}, further making
them more attractive, and easier to both adopt and use.

\input{tex/intro/parametric-operations}
\input{tex/intro/constraints}
\input{tex/intro/examples}
\input{tex/intro/algorithmic-design}
