% !TeX root = ../../../main.tex
\subsection{Computational Geometry Algorithms Library}%
\label{sec:solution.impl.cgal}

\Ac{CGAL} is a software project that provides easy access to efficient and
reliable geometric algorithms in the form of a C++ library.  It is considered
the industry's \textit{de facto} standard geometric library, used in well-known
projects such as OpenSCAD.  It is also a very mature software library with
decades of Ph.D.-grade research results, still being actively maintained to this
day.  Being an open-source project, one can easily contribute to it by reporting
issues in the software as well as directly submitting patches.\footnote{The
library's source is hosted on GitHub at \url{https://github.com/CGAL/cgal}.  To
illustrate the ease with which one can contribute to the project, here is a pull
request the author submitted: \url{https://github.com/CGAL/cgal/pull/4705}.}

These factors, among others, justify our choice for our solution's
\geomlibrary{} component: we chose \ac{CGAL} because of its comprehensiveness
and decades of work invested in the production of a piece of highly mature
software, as well as the critical mass of maintainers behind it.  That is not to
say less mature software cannot be used in its stead, though it is unlikely it
can match \ac{CGAL}, be it in terms of performance, quality, or breadth.

\ac{CGAL} offers a multitude of data structures and algorithms, such as
triangulations, Voronoi diagrams, and convex hull algorithms, to name a few.
The library is broken up into three parts~\cite{CGAL:5.3:23LGK}:
\begin{enumerate}
  \item The kernel, which consists of geometric primitive objects and operations
  on these objects.  The objects are represented both as
  \begin{enumerate*}
    \item stand-alone classes parameterized by a representation class that
    specifies the underlying number types used for computation, and as
    \item members of the kernel classes, which allows for more flexibility and
    adaptability of the kernel;
  \end{enumerate*}
  \item Basic geometric data structures and algorithms, parameterized by traits
  classes that define the interface between the data structure or algorithm and
  the primitives they use;
  \item Non-geometric support facilities, such as circulators, random sources,
  and I/O support for debugging and for interfacing \ac{CGAL} with various
  visualization tools.
\end{enumerate}

Kernels in \ac{CGAL} are parametric, enabling the combination of kernels with
exact predicates and exact constructions or inexact constructions.  The latter
provide exact predicates and are faster than the former, but may produce inexact
results due to \textit{roundoff} errors.  In practice, however, inexact
construction kernels suffice for most of \ac{CGAL}'s algorithms.

\Cref{lst:solution.impl.cgal.pas} showcases an example of a very simple
\ac{CGAL} program, demonstrating the construction of points and a segment, and
performing some basic operations on them.

\begin{listing}[htbp]
  \caption[CGAL: Three points and one segment]{
    An example CGAL program illustrating how to construct some points and a line
    segment, and perform some basic operations on them.  It uses
    \mintinline{c}{double} precision floating point numbers for Cartesian
    coordinates.}\label{lst:solution.impl.cgal.pas}
  \inputminted{cpp}{cpp/points_and_segments.cpp}
\end{listing}

As mentioned, geometric primitive types are defined in the kernel.  The kernel
chosen in the example uses \texttt{double} precision floating point numbers for
the Cartesian coordinates of the point.

We can also see some predicates, such as testing the orientation of three
points, and constructions, like the distance\footnote{It is worth noting
\ac{CGAL} does \texttt{not} compute the absolute distance, offering instead to
compute the squared distance, as this avoids the additional square root
computation.  This preserves exactness and eliminates a potentially unnecessary
heavy computation.} and midpoint computation.  Predicates typically produce a
boolean logical value or one of a discrete set of possible results, whereas
constructions produce either a number or another geometric entity.

It is worth noting that floating point-based geometric computation can lead to
surprising results since we are relying on inexact constructions.  If one must
ensure that the numbers get interpreted at their full precision, all one has to
do is pick a kernel with exact constructions.  Revisiting
\cref{lst:solution.impl.cgal.pas}, it is as simple as switching the
\texttt{Simple\_cartesian} kernel with one the provides exact constructions,
e.g., \texttt{Exact\_predicates\_exact\_constructions\_kernel} or \texttt{Epeck}
for short.

Unfortunately, \ac{CGAL} is a terribly complex library under the hood,
presenting many challenges when it comes to mapping it to the Julia language.
Firstly, it is a C++ library.  Despite Julia's native capabilities for
interoperating with C, there's additional work to be done to reach C++ code.
Secondly, is problem of memory management, which differs between C/C++ and
Julia, potentially leading to memory leaks and other related issues if not
properly tended to.  Finally, \ac{CGAL} makes extensive use of C++ templates,
proving sometimes difficult to transparently map some of its constructs.

In the next section, we go over how we overcame these issues.
